% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TeX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,MMMyyyy,nonstop]{simpleresumecv}
% Class options:
% a4paper, letterpaper, draft, nonstop
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{David Lavy}
\newcommand{\CVTitle}{David Lavy's ticket for awesome job}
%\newcommand{\CVNote}{CV compiled on {\today} for Acme Corporation}
\newcommand{\CVWebpage}{davidlavy88.github.io}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

\newcommand*{\TitleFont}{%
      \usefont{\encodingdefault}{\rmdefault}{bx}{n}%
      \fontsize{20}{24}%
      \selectfont}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{\TitleFont \CVAuthor}

\begin{subtitle}
%\href{https://www.google.com/maps/place/1086+Commonwealth+Ave,+Boston,+MA+02215,+USA}
%{1086 Commonwealth Avenue, Apt 102, Boston 02215, USA}
%\par
\href{\CVWebpage}
{\CVWebpage}
\,\SubBulletSymbol\,
\href{mailto:david.lavy88@gmail.com}
{david.lavy88@gmail.com}
\par
+1\,(617)\,820-9523
\,\SubBulletSymbol\,
\href{https://github.com/davidlavy88}
{github.com/davidlavy88}

\end{subtitle}

\begin{body}

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OBJECTIVES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Objectives}
{Objectives}
{PDF:Objectives}

To obtain a challenging position in a creative, technology-driven organization where I can apply my education, 7 years of expertise in the robotics field and implement my innovative ideas, skills and creativity for accomplishing compelling projects.
%\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Skills}
{Skills}
{PDF:Skills}

\GapNoBreak
\BulletItem
\textbf{Programming Languages}: \textit{C/C++, Python, MATLAB/Octave/Simulink, C\#, Java, HTML/CSS}
\SubBulletItem
7 years of experience designing, tuning, debugging and testing code in different languages.
\BulletItem
\textbf{Robotics Libraries}: \textit{OpenCV, PCL, CUDA, OpenGL}
\SubBulletItem
5 years of expert knowledge using computer vision packages and algorithms applied to simulated and real robots.
\BulletItem
\textbf{Robotics Frameworks}: \textit{ROS, Gazebo, MORSE, NAOqi}
\SubBulletItem
Proven ability to create robotic applications in different middlewares and simulators.
\BulletItem
\textbf{Source control}: \textit{Git, Github}
\SubBulletItem
Experience using source control to track, maintain and contribute source code for different projects.
\BulletItem
\textbf{IDE \& Build tools}: \textit{QtCreator, Eclipse, Codeblocks, Visual Studio, CMake, Make}
\SubBulletItem
7 years of experience developing application software for different platforms in many robotic areas.
\BulletItem
\textbf{Operating Systems}: \textit{Linux, Embedded Linux, Windows, VirtualBox, QEMU}
\SubBulletItem
Hands on experience developing and testing software in different operating systems and emulators.
\BulletItem
\textbf{Embedded Systems}: \textit{Arduino, Gumstix, Raspberry Pi}
\SubBulletItem
Expertise programming microcontrollers and single-board computers to design embedded and robotics applications.
\BulletItem
\textbf{Writing}: {\TeX}, {\LaTeX}
\SubBulletItem
Strong skills preparing and designing technical and scientific documents.
\BulletItem
\textbf{CAD Tools}: \textit{AutoCAD, SolidWorks}
\SubBulletItem
Proficient with 3 years of experience modeling mechanical parts as well as electrical design.
\BulletItem
\textbf{Office}: \textit{Microsoft Word, PowerPoint, and Excel. SalesForce, SAP By Design}
\SubBulletItem
Skillful in using office tools to create reports, presentations and supply chain management.

%%%%%%%%%%%%%%%%%%%%%%%%%%
%% REASEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Research Experience}
{Research Experience}
{PDF:ResearchExperience}
%\iffalse
\href{https://github.com/davidlavy88/EMOpticalSensing/blob/master/EC503_EM_Optical_Sensing_Final_Report.pdf}
{\textbf{E-M Algorithm for optical position sensing}}
\hfill
Boston University, \textit{2016}

\GapNoBreak
\BulletItem
Investigated the Expectation-Maximization algorithm as a tool for estimating signal positions on a two-dimensional detector for a single beam when detection counts are low. A multiple beam tracking was also considered using Kalman Filter and the Hungarian algorithm.
\GapNoBreak
%\fi
%\iffalse
\href{https://github.com/davidlavy88/NAOGumstix/blob/master/ec535FinalReport.pdf}
{\textbf{Remote control of NAO using a Gumstix Board}}
\hfill
Boston University, \textit{2016}

\GapNoBreak
\BulletItem
Designed a remote control for the NAO humanoid robot using a Gumstix board. An LCD serves as a UI which sends data from the Gumstix to a PC via Bluetooth. The PC will process the data into executable commands which will send to the robot via WiFi.
\GapNoBreak
%\fi

\href{http://www.bu.edu/vip/files/pubs/reports/DLTM15-06buece.pdf}
{\textbf{Autonomous navigation with NAO}}
\hfill
Boston University, \textit{2015}

\GapNoBreak
\BulletItem
Designed a navigation system using the visual information from the 2 cameras mounted on the NAO humanoid robot, as well as its sonar sensors, that seeks to find a ball, navigate to it, and kick it.
\GapNoBreak
%\textit{Keywords}: Python, OpenCV, NAOqi, Linux

\BigGap
\href{http://www.bu.edu/vip/files/pubs/reports/DLDP15-03buece.pdf}
{\textbf{Virtual shape recognition using Leap Motion}}
\hfill
Boston University, \textit{2015}

\GapNoBreak
\BulletItem
Designed a system to recognize hand drawing gestures of numerical letters in the air using a gesture-capturing sensor and  output the corresponding values.
\GapNoBreak
%\textit{Keywords}: C++, MATLAB, OpenCV, Machine Learning, Linux, Leap Motion SDK

\href{https://docs.google.com/presentation/d/1328Qvm9VlAZadwlNoU3n5m1REY36m_hGcakSYlxW2vM/edit?ts=565d2938#slide=id.p}
{\textbf{Facial identification using a multilayer perceptron}}
\hfill
Boston University, \textit{2015}

\GapNoBreak
\BulletItem
Implemented and trained a neural network which classifies people based on faces. The system can take new people and new faces and extend its information to learn to recognize new people.
\GapNoBreak
%\textit{Keywords}: Python, OpenCV, Machine Learning, Linux, PyBrain

\BigGap
\textbf{Modelling and Control of UAV using SLAM}
\hfill
Univ. Nacional de Ingenieria, \textit{2011}

\GapNoBreak
\BulletItem
Modelled a quad-rotor using linear control. Developed an artificial vision system with a mounted Kinect and used a navigation and mapping technique to make the vehicle autonomous.
\GapNoBreak
%\textit{Keywords}: Python, C++, MATLAB, OpenCV, ROS, Linux

\BigGap
\href{https://github.com/davidlavy88/resume/blob/master/Paper/paper-mt-517.pdf}
{\textbf{Design and modelling of a 4 DOF Robotic Arm}}
\hfill
Univ. Nacional de Ingenieria, \textit{2010}

\GapNoBreak
\BulletItem
Simulation of a 4 DOF KUKA Robotic Arm in Simulink (MATLAB) using linear, nonlinear and fuzzy control. The robot was designed using SolidWorks and then exported to Simulink.
\GapNoBreak
%\textit{Keywords}: MATLAB, Simulink, SolidWorks, Artificial Intelligence

%\begin{detail}
%\SubBulletItem
%Project:
%
%\end{detail}

%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORKING EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Work Experience}
{Work Experience}
{PDF:WorkExperience}

\textbf{Robotics Investigation Engineer}
\hfill
\DatestampYMD{2016}{05}{28} --
Present 
\begin{detail}
\normalsize{ \href{https://www.ald.softbankrobotics.com/en}
{\textit{Softbank Robotics America}},
Boston, Massachusetts, USA }
\end{detail}

\GapNoBreak
\BulletItem
Investigate and solve the most impacting issues on the market in the last 3 months. 
\BulletItem
Report and follow the root cause of the defect in the humanoid robot Pepper. 
\BulletItem
Maintain and update a thorough documentation of all the investigation activity related to hardware and software.

\BigGap
\textbf{Robotics Repair Engineer for the Americas}
\hfill
\DatestampYMD{2013}{04}{01} --
\DatestampYMD{2016}{05}{27}
\begin{detail}
\normalsize{ \href{https://www.aldebaran.com/en}
{\textit{Aldebaran Robotics/Softbank Group}},
Boston, Massachusetts, USA }
\end{detail}

\GapNoBreak
\BulletItem
Repair hardware and software issues for NAO and Pepper humanoid robots for all North and South America. 
\BulletItem
Achieved fastest repair time worldwide since January 2015 for our Boston office, increasing customer satisfaction and overall KPI.
\BulletItem
Teach technical training sessions for distributors and customers about how to use and program the robots.
\BulletItem
Provide software and hardware assistance at trade shows and special events, in the USA, Mexico, France and Brasil, including the international competition Robocup.
\BulletItem
Trained at the headquarters in Paris and the Tokyo office about hardware and software repair for NAO and Pepper humanoid robots.

\BigGap
\textbf{Cafeteria Manager}
\hfill
Winter 2010 --
Winter 2011 --
Winter 2013
\begin{detail}
\normalsize{ \href{http://www.patspeak.com/}
{\textit{Pats Peak Ski Area}},
Henniker, New Hampshire, USA }
\end{detail}

\GapNoBreak
\BulletItem
Managed and trained a staff of 30 individuals in the cafeteria at a busy ski area.
\BulletItem
Ensured that operations ran smoothly and efficiently.

\BigGap
\textbf{Automation Engineer}
\hfill
\DatestampYMD{2012}{03}{01} --
\DatestampYMD{2012}{08}{30}
\begin{detail}
\normalsize{ \href{http://www.alicorp.com.pe/alicorp/index.html}
{\textit{Alicorp}},
Callao, Lima, Peru }
\end{detail}

\GapNoBreak
\BulletItem
Supervised the electric and automatized engineering operations within two production factories.
\BulletItem
Managed the engineering and automation design of one of the mills. Facilitated communication and transport between factories, optimizing daily operations.

\BigGap
\textbf{Intern}
\hfill
\DatestampYMD{2011}{05}{01} --
\DatestampYMD{2011}{10}{31}
\begin{detail}
\normalsize{ \textit{Mafersa},
Pueblo Libre, Lima, Peru }
\end{detail}

\GapNoBreak
\BulletItem
Team member responsible for the design of electrical installations within residential and commercial buildings.
\BulletItem
Greatly improved knowledge of electrical design in AutoCAD and programming in Excel Macros.

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section
{Education}
{Education}
{PDF:Education}

\href{http://www.bu.edu/}
{\textbf{Boston University}},
Boston, Massachusetts, USA

\GapNoBreak
\BulletItem
Master of Science (M.Sc.) in
\href{http://www.bu.edu/ece/}
{Electrical Engineering}
\hfill
\DatestampYMD{2014}{09}{01} --
\DatestampYMD{2016}{05}{15}
\begin{detail}
\SubBulletItem
Cumulative GPA: 3.89 / 4.0
\end{detail}
\BulletItem
Graduate Coursework: Digital Signal/Image/Video Processing, DSP, Stochastic Processes, Machine Learning, Embedded Systems, Linux Kernels, Speech Processing, Signal Detection/Estimation, Pattern Recognition

\BigGap
\href{http://www.uni.edu.pe/}
{\textbf{Universidad Nacional de Ingenieria}},
Lima, Peru

\GapNoBreak
\BulletItem
Bachelor of Science (B.S.) in
\href{http://www.fim.uni.edu.pe/}
{Mechatronics Engineering}
\hfill
\DatestampYMD{2006}{09}{1} --
\DatestampYMD{2011}{08}{31}
\begin{detail}
\SubBulletItem
Ranked 10/46 in graduating class.
\SubBulletItem
Cumulative GPA: 3.75 / 4.00
\end{detail}
\BulletItem
Undergraduate Coursework: Robotics Control, Artificial Intelligence, Computer Vision, HMI, Programming Languages, Algorithms, Videogame Programming

%%%%%%%%%%%%%%%%%%%%%%%
%% HONORS AND AWARDS %%
%%%%%%%%%%%%%%%%%%%%%%%

\section
{Honors \newline
\& Awards}
{Honors and Awards}
{PDF:HonorsandAwards}

\GapNoBreak
\BulletItem
Placed $2^{nd}$ in CONEIMERA (\textit{National Congress of Mechanical and Electrical Engineering}) 2011 (Lima, Peru)
\SubBulletItem
Project Title: \textit{Linear Modeling and Control of UAV using Autonomous Navigation}
\GapNoBreak
\BulletItem
Travel grant to attend CONEIMERA 2011 from Universidad Nacional de Ingenieria
\GapNoBreak
\BulletItem
Placed $2^{nd}$ in CONEIMERA 2010 (Lima, Peru)
\SubBulletItem
Project Title: \textit{Security Systems for Access Control Using RFID Technology}
\GapNoBreak
\BulletItem
Travel grant to attend CONEIMERA 2010 from Universidad Nacional de Ingenieria
\GapNoBreak
\BulletItem
Certificate of recognition for highest academic performance in the Mechatronic Engineering Department at Universidad Nacional de Ingenieria, 2008

%%%%%%%%%%%%%%%%%%%%%
%% CERTIFICATES %%
%%%%%%%%%%%%%%%%%%%%%

\section
{Certificates}
{Certificates}
{PDF:Certificates}

\GapNoBreak
\BulletItem
\href{https://github.com/davidlavy88/resume/blob/master/Certificates/robotic-car-certificate.pdf}
{Programming a Robotic Car}
\hfill
\textbf{Udacity}
\GapNoBreak
\BulletItem
\href{https://github.com/davidlavy88/resume/blob/master/Certificates/artificial-intelligence-certificate.pdf}
{Introduction to Artificial Intelligence}
\hfill
\textbf{Udacity}
\GapNoBreak
\BulletItem
\href{https://github.com/davidlavy88/resume/blob/master/Certificates/machine-learning-certificate.pdf}
{Machine Learning}
\hfill
\textbf{Coursera}
\GapNoBreak
\BulletItem
\href{https://github.com/davidlavy88/resume/blob/master/Certificates/nn-for-ml-certificate.pdf}
{Neural Networks for Machine Learning}
\hfill
\textbf{Coursera}
\GapNoBreak
\BulletItem
\href{https://github.com/davidlavy88/resume/blob/master/Certificates/writing-in-sciences-certificate.pdf}
{Writing in the Sciences}
\hfill
\textbf{Coursera}
\GapNoBreak
\BulletItem
\href{https://github.com/davidlavy88/resume/blob/master/Certificates/cs184-certificate.pdf}
{Foundations of Computer Graphics}
\hfill
\textbf{edX}

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\section
{Languages}
{Languages}
{PDF:Languages}

\GapNoBreak
\BulletItem
English: Fluent (speaking, reading, writing)
\GapNoBreak
\BulletItem
Spanish: Fluent (speaking, reading, writing)
\GapNoBreak
\BulletItem
French: Basic (speaking, reading, writing)
\GapNoBreak
\BulletItem
Japanese: Basic (speaking, reading, writing)

%%%%%%%%%%%%%%%
%% WORK STATUS %%
%%%%%%%%%%%%%%%

\section
{Work Status}
{Work Status}
{PDF:WorkStatus}

Legally authorized to work in the United States.

%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

%\section
%{Interests}
%{Interests}
%{PDF:Interests}
%
%Digital photography,
%typography,
%swimming.
%
%%%%%%%%%%%%%%%%%
%%% REFERENCES %%
%%%%%%%%%%%%%%%%%
%
%\section
%{References}
%{References}
%{PDF:References}
%
%\BulletItem
%\textbf{Professor Jonathan Public}
%\newline
%Professor of Geology and Mechanical Engineering
%\newline
%First American University
%\begin{detail}
%\SubItem
%1000 First Avenue, Springfield, Massachusetts 22222, USA
%\newline
%\href{mailto:jonathanpublic@example.com}
%{jonathanpublic@example.com}
%\,\SubBulletSymbol\,
%+1\,(555)\,222-2222
%\end{detail}
%
%\Gap
%\BulletItem
%\textbf{Dr Alice Bob Carol}
%\newline
%Director, Research \& Development
%\newline
%Alpha Engineering Firm
%\begin{detail}
%\SubItem
%20 North Street, Oakland, Ohio 33333, USA
%\newline
%\href{mailto:alicebobcarol@example.com}
%{alicebobcarol@example.com}
%\,\SubBulletSymbol\,
%+1\,(555)\,333-3333
%\end{detail}
\end{body}

\end{document}
